### 2020-04-22 final_report/data.tex
add some TODOs and sklearn ref

@@

To pursue linear feature extraction, principal component analysis (PCA) \cite{Jolliffe2016} was performed via scikit-learn on a set of 300,000 uniform samples of the MC TBR model.

>>>>

% TODO: here maybe mention desirable effects of dim. red. (e.g. speedup,
% simplification of the problem, better convergence...)

@@

To pursue linear feature extraction, principal component analysis (PCA)
\cite{Jolliffe2016} was performed via SciKit Learn~\cite{scikit-learn} on a set
of \num{300000} uniform samples of the MC TBR model. % TODO:which run? batch range?
